# Planetary Boundaries indicators

## PB 1: Climate Change Indictator 


### Atmospheric CO2 concentration 

```{r}
showLinePlotsWithZones(
  data,
  "MAGICC7 AR6|Atmospheric Concentrations|CO2|67.0th Percentile",
  # from Richardson et al 2023
  safePB = 350,
  highRisk = 450
)
```


### Radiative Forcing 

```{r}
showLinePlotsWithZones(
  data,
  "MAGICC7 AR6|Effective Radiative Forcing|Basket|Anthropogenic|67.0th Percentile",
  # from Richardson et al 2023
  safePB = 1,
  highRisk = 1.5
)
```


### Global Mean Surface Temperature  

```{r}
showLinePlotsWithZones(
  data,
  "MAGICC7 AR6|Surface Temperature (GSAT)|67.0th Percentile",
  # as from Feli (not in Richardson or Steffen)
  safePB = 1,
  highRisk = 2
)
```


## PB 2: Ozone 

van Vuuren et al (2025) used CMIP6 data, mostly over the Antarctica region 

## PB 3: Aerosols 

van Vuuren et al (2025) calculates something, and plug it into the FASST model 

## PB 4: Ocean Acidification 

```{r}
# This is the approach from van Vuuren, MAGICC also has net transport to ocean, maybe that is more exact?
a <- -5e-8 # vanVuuren value was given by Gt, so I changed to exponent from e-5 to e-8 to adjust to our values in Mt
b <- 8.0957

data2 <- data %>%
  dplyr::mutate(
    value = dplyr::if_else(
      variable == "Emi|CO2|Cumulated",
      a * value + b,
      value
    ),
    variable = dplyr::if_else(
      variable == "Emi|CO2|Cumulated",
      "pH",
      variable
    ),
    unit = dplyr::if_else(
      variable == "pH",
      "pH",
      unit
    )
  )

showLinePlotsWithZones(
  data2,
  "pH",
  # as from Feli (not in Richardson or Steffen)
  safePB = 8.01,
  highRisk = 7.94,
  ylim = c(7.85,8.1)
)
```


## PB 5: Nitrogen Balance 

### Nitrogen Surplus 

```{r}
showLinePlotsWithZones(
  data,
  "Planetary Boundary|Nitrogen|Agricultural Nitrogen surplus",
  # this is taken from Feli paper, Richardson et al 2023 state 62, and upper limit 82
  safePB = 61,
  highRisk = 84
)
```



## PB 6: Phosphorus Balance 

## PB 7: Freshwater Use 

### Freshwater Consumption 

```{r}
showLinePlotsWithZones(
  data,
  "Planetary Boundary|Freshwater|Water consumption",
  # why is this so low? 
  safePB = 2800,
  highRisk = 4500
)
```


## PB 8: Land System Change / Land Cover 

### Forest Cover 

```{r}
showLinePlotsWithZones(
  data,
  "Planetary Boundary|Land|Forest cover",
  safePB = 4790,
  highRisk = 3449
)
```


  


## PB 9: Biosphere Integrity

<!-- 
  "Planetary Boundary|Biosphere|Share of intact land relative to total land area (unitless)",
  "Planetary Boundary|Biosphere|Share of land area that satisfies landscape target (unitless)", -->

### Share of intact land relative to total land area 

```{r}
showLinePlotsWithZones(
  data,
  "Planetary Boundary|Biosphere|Share of intact land relative to total land area",
  # from Feli 
  safePB = 0.6,
  highRisk = 0.5,
  ylim = c(0.35,0.7)
)
```


### Share of land area that satisfies landscape target 

```{r}
showLinePlotsWithZones(
  data,
  "Planetary Boundary|Biosphere|Share of land area that satisfies landscape target",
  # from Feli 
  safePB = 1,
  #highRisk = 4500,
  ylim = c(0.7,1.05)
)
```

